---
title: "Week 1 Markdown Demo"
author: "Kellen Sorauf"
date: "March 1, 2022"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
library(markdown)
```

### Some helpful R commands to get you started:

* To run code press ctrl+enter - also works for multiple lines
* rm() removes object from global environment
* To search for help on a function use: ?function
* To install packages use: install.packages('packageName')
* To upate all packages use: update.packages()


### Some helpful R Markdown commands to get you started:

Here is a [link](https://rmarkdown.rstudio.com/lesson-1.html) to a R Markdown tutorial

* To create a code chunck ```{r title, args}
* each *title* must be uniquely named
* To end a code chunck ```
* Press green play error button on top right of code chuck to run that line of code.

#### args that can be included in code chunk:

* *include = FALSE* prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.
* *echo = FALSE* prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.
* *message = FALSE* prevents messages that are generated by code from appearing in the finished file.
* *warning = FALSE* prevents warnings that are generated by code from appearing in the finished.
* *fig.cap = "..."* adds a caption to graphical results.

* Knit button knits document (I suggest using HTML).
* Use gear button to Preview in Viewer Pain

# Let's load some data
```{r load_data}
# cars is a built in data file
dt = cars
```

## You can plot data 

You can also embed plots, for example:

```{r plot, echo=FALSE}
plot(dt$speed, dt$dist)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
